### 2015-11-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update DelCo2012 work

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
	\label{fig:CAFS_Water_Comp_7_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
	\label{fig:CAFS_Water_Comp_SS_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Full Back Position}
	\label{fig:CAFS_Water_Comp_SS_full}
\end{figure}

>>>>

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
	\label{fig:CAFS_Water_Comp_7_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
	\label{fig:CAFS_Water_Comp_SS_mid}
\end{figure}
